---
title: "STAT 327 Homework 3"
output: html_document
---

We'll grade your homework by

* opening your "hw3.Rmd" file in RStudio
* clicking "Knit HTML"
* reading the HTML output
* reading your "hw3.Rmd"

You should write R code anywhere you see an empty R code chunk. You
should write English text anywhere you see "..."; please surround it
with doubled asterisks (`**...**`) so that it will show up as boldface
and be easy for us to find.

Include reasonable labels (titles, axis labels, legends, etc.) with
each of your graphs.

Name: Richard Yang  

Email: gyang79@wisc.edu

We'll use data on housing values in suburbs of Boston. They are in an
R package called "MASS." (An R package is a collection of code,
data, and documentation. "MASS" refers to the book "Modern Applied
Statistics with S." R developed from the earlier language, S.) The
MASS package comes with the default R installation, so it's already on
your computer.  However, it's not loaded into your R session by
default. So we'll load it via the `require()` command (there's nothing
for you to do here):

```{r}
require("MASS")
```

Run `?Boston` (outside this R Markdown document) to read the help page for the `Boston` data frame.

Convert the `chas` variable to a factor with labels "off" and "on" (referring to the Charles river).

```{r}
boston <- Boston
boston$chas <- factor(Boston$chas,levels=c(0,1),labels=c('off','on'))
```

How many rows are in the Boston data frame? How many columns?

```{r}
dim(boston)
```
**So there are 506 rows and 14 columns in the Boston data.**
What does a row represent?
**The row represents some features of each suburb.**

What does a column represent?

**The column represents one specific feature of all suburbs in Boston.**

Make a density plot (with rug) of tax rates.

```{r}
plot(density(boston$tax),main = "Density of tax rate")
rug(boston$tax)
```

Describe the shape of the distribution of tax rates.

**The density has the mountain shape of double peaks,which are 300 and 700 respectively.**

Note that the distribution shape doesn't make sense in light of the rug representation of the data. Make a histogram of the tax rates.

```{r}
hist(boston$tax)
```

Why is the second peak of the density plot so large? In what way is the rug representation of the data inadequate? Write a line or two of code to figure it out, and then explain it.

```{r}
stripchart(boston$tax,method = 'jitter',main='stripchart of tax',xlab = 'tax')

```

**We plot the stripchart, and from this graph, we know there are lots of duplicate values. So in fact, it's reasonable to have such a second peak.**

**And rug may cause some confusion if there are lots of duplicate values, which would only plot seldom rug.**
...

Make a barplot of "chas".

```{r}
counts= table(boston$chas)
barplot(counts,main = 'Barplot of chas')
```

How many neighborhoods are on the Charles river?

```{r}
counts
```

**There are 35 neighborhoods are on the Charles river.**

Make a single graph consisting of three plots: 

* a scatterplot of "nox" on the y-axis vs. "dis" on the x-axis 
* a (vertical) boxplot of "nox" left of the scatterplot's y-axis
* a (horizontal) boxplot of "dis" below the scatterplot's x-axis

Hint: use `layout()` with a 4x4 matrix, using the top-right 3x3 corner
for the scatterplot, leaving the bottom-left 1x1 corner blank, and
using the other parts for the boxplots.

(An optional challenge, worth 0 extra credit points: remove the axis
and plot border from each boxplot.)

```{r, fig.width=7, fig.height=7}
m<-matrix(data=c(1,2,2,2,1,2,2,2,1,2,2,2,0,3,3,3),nrow = 4, byrow = T)
layout(m)
boxplot(boston$nox,main= 'Concentration nitroxide')
plot(boston$dis,boston$nox,axes=F,main = 'The relationship between distance to employment centers and nitrogen oxides' )
boxplot(boston$dis,horizontal = T,main='The distance to employment centers')
layout(matrix(data=1,nrow=1))

```

Look into the highest-crime neighborhood by making a single graph of one column of three rows:

* Find the row number, r, of the neighborhood with the highest "crim".
* Make a density plot of "crim". Include a rug to show the data.
* Add a red circle at (x, y) = (max crime rate, 0) to make this maximum crime rate stand out.
* Make a density plot with rug of "medv", adding a red circle at (x, y) = (medv[r], 0) to see what medv corresponds to the highest crime rate.
* Repeat the last step for "ptratio".

```{r}
r=which.max(boston$crim)
n<- matrix(c(1,2,3),nrow=3)
layout(n)
plot(density(boston$crim),main='Density of crime')
points(max(boston$crim),0,pch=1,col='red',cex=3)
plot(density(boston$medv),main = 'Density of median house value')
points(boston$medv[r],0,pch=1,col='red',cex=3)
plot(density(boston$ptratio),main = 'Density of pupil-teacher ratio')
points(boston$ptratio[r],0,pch=1,col='red',cex=3)
```

What do you notice about the ptratio and medv for the highest-crime neighborhood?

**I find the neighborhood with highest crime rate has low house value and relatively high pupil-teacher ratio, which indicates the poverty and lack of education.**

**So it's quite reasonable to has such phenomenon in this place.**
...
